\documentclass[11pt]{article}
\usepackage{fullpage}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage[top=0.9in, bottom=0.9in, left=0.9in, right=0.9in]{geometry}

\textheight=9.0in
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\urlstyle{same}
\begin{document}

\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
	\textbf{Ankit Ahuja} & \\
	ahuja.ankit@gmail.com \\
	http://ankitahuja.com \\
\end{tabular*}
\vspace{0.2in}

\textbf{Experience}
\begin{itemize}
	\setlength{\parskip}{2mm}%
	\item
		\begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
			\textbf{Grammarly, New York} & August 2022 - Present\\
		\end{tabular*}
		Staff Software Engineer \\
		\vspace{3 mm}
		\begin{itemize}
			\item Leading technical strategy and frontend architecture for Grammarly's agent-based assistant. Aligning 10+ engineers across 3 teams and driving a unified implementation across web and native platforms.
			\item Reduced text input lag by 90\% in third-party editors when using the Grammarly browser extension. This included designing a new UX which lowered extension disable rate by 9\%. 
			\item Led a 4-person team to eliminate 98\% of memory leaks and reduce the extension's memory footprint by 30\%, significantly improving performance on less powerful machines.
			\item Defined and implemented lab and field performance metrics for Grammarly extension, including Interaction To Next Paint (INP), enhancing observability and preventing performance regressions.
			\item Designed and implemented an improved Grammarly integration with Overleaf, increasing 2-week retention rate by 61.3\%.
		\end{itemize}
	\end{itemize}
		
\begin{itemize}
	\setlength{\parskip}{2mm}%
	\item
		\begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
			\textbf{Coursera, Mountain View} & October 2014 - December 2021\\
		\end{tabular*}
		Senior Staff Software Engineer \\
		\vspace{3 mm}
		\begin{itemize}
			\item Led the development of Coursera's design system to ensure product features meet accessibility standards (WCAG 2.2 AA) and use consistent design patterns. It helped improve code quality and developer productivity by reusing components and APIs. 20+ designers and 60+ engineers spread across the USA, Canada, UK, and Dubai used the system. 
			
			\item Led the adoption and migration to TypeScript at Coursera to enable type-safety in the entire front-end codebase. The majority of the codebase (>50\%) was in TypeScript, and it became the default programming language used by 60+ engineers.
			
			\item Led the design, prototyping, and development of WYSIWYG content authoring tools for instructors, enabling them to author and publish all courses on Coursera.
			
			\item Built key product features including course rating systems, interactive video transcripts, in-browser coding and framework to deliver realtime tips to learners.
			
			\item Helped define long-term architecture, plan execution on engineering-wide initiatives, and perform technical design reviews as part of the architecture group at Coursera.

			% \item Developed an end-to-end testing framework for Coursera using Puppeteer and Jest. It became an essential tool to prevent product regressions on 100+ critical product flows.
		\end{itemize}

	\item
		\begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
			\textbf{LinkedIn, Mountain View} & July 2013 - October 2014\\
		\end{tabular*}
		Software Engineer \\
		\vspace{3 mm}
		\begin{itemize}
			\item Led the design and implementation of MVC-based frontend architecture for Sales Navigator. Built key product features including login, onboarding and search.
		\end{itemize}

	\item
		\begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
			\textbf{Department of Computer Science, Virginia Tech} & August 2011 - May 2013\\
		\end{tabular*}
		Graduate Research Assistant \\
		\vspace{3 mm}
		\begin{itemize}
			\item Built Contextinator for my Master's Thesis (\emph{\url{http://ankitahuja.com/thesis/}}), a browser extension that lets users divide their web browsing sessions into projects.
		\end{itemize}

	\item
		\begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
			\textbf{Khan Academy, Mountain View} & May - August 2012\\
		\end{tabular*}
		Software Developer Intern\\
		\vspace{3 mm}
		\begin{itemize}
			\item Designed and implemented the client and backend for user discussions displayed in different contexts on khanacademy.org. 
		\end{itemize}
\end{itemize}

\textbf{Side Projects}

\begin{itemize}
	\setlength{\parskip}{2mm}

	\item
		\begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
			\textbf{Stylebot} - \emph{\url{https://stylebot.dev/}}
		\end{tabular*} \\

		\vspace{3 mm}

		Lets users manipulate the appearance of any webpage through a WYSIWYG interface in the web browser. More than 200,000 active users and featured on Chrome and Firefox.

  \item
    \begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
      \textbf{Vue Photos} - \emph{\url{https://ankitahuja.com/vue-photos}}
    \end{tabular*} \\

    \vspace{3 mm}

    A minimal Vue library to display self-hosted photo albums.

\end{itemize}

\vspace{0.1in}

\textbf{Education}

\begin{itemize}
	\setlength{\parskip}{2mm}%
	\item
		\begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
			\textbf{M.S. Computer Science} & May 2013 \\
		\end{tabular*}
		Specializing in Human Computer Interaction \\
		Virginia Tech, Blacksburg, VA \\
		GPA: 3.95 / 4.0 \\

	\item
		\begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
			\textbf{B.E. Computer Science and Engineering} & August 2010 \\
		\end{tabular*}
		SBIT, MDU, India \\

\end{itemize}

\vspace{0.1in}

\textbf{Talks and Writing}

\begin{itemize}
	\setlength{\parskip}{2mm}%

	\item
		\textbf{Improving End-to-End Testing at Coursera using Puppeteer and Jest} - \emph{\url{https://medium.com/coursera-engineering/improving-end-to-end-testing-at-coursera-using-puppeteer-and-jest-5f1bac9cd176}}
		
	\item
		\textbf{Make editing courses on Coursera fun} - \emph{\url{https://medium.com/coursera-engineering/make-editing-courses-on-coursera-fun-bf6635f44cbf}}

	\item
		\textbf{Contextinator - Project-based Management of Personal Information
		on the Web} - Ankit Ahuja, Ben Hanrahan and Manuel A. Perez-Quinones: WEBIST 2014

	\item
		\textbf{Virtual Town Square - Building a Local Information Ecosystem} - Ankit Ahuja: Center for HCI Seminar Series, Virginia Tech, Blacksburg, VA; Feb 2013

	\item
		\textbf{Designing a Location-Based Interface for a Hyper-local News Aggregator} - Ankit Ahuja, Andrea Kavanaugh: Open Locast U Symposium, MIT Mobile Experience Lab, MIT, Cambridge, MA; Jan 2013	
\end{itemize}

\end{document}
