% My LaTeX resume
%
% Derived from Matthew M. Boedicker <matthewm@boedicker.org>'s template
%

\documentclass[11pt]{article}
\usepackage{fullpage}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage[top=0.9in, bottom=0.9in, left=0.9in, right=0.9in]{geometry}

\textheight=9.0in
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\urlstyle{same}
\begin{document}

  \begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
    \textbf{Ankit Ahuja} & \\
    ahuja.ankit@gmail.com \\
    http://ankitahuja.com \\
  \end{tabular*}
  \vspace{0.2in}

  \textbf{Education}

  \begin{itemize}
    \setlength{\parskip}{2mm}%
    \item
    \begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
      \textbf{M.S. Computer Science} & May 2013 \\
    \end{tabular*}
      Specializing in Human Computer Interaction \\
      Virginia Tech, Blacksburg, VA \\
      GPA: 3.95 / 4.0 \\

    \item
    \begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
      \textbf{B.E. Computer Science and Engineering} & August 2010 \\
    \end{tabular*}
    SBIT, MDU, India \\

  \end{itemize}

  \vspace{0.1in}

  \textbf{Experience}
  \begin{itemize}
    \setlength{\parskip}{2mm}%
    \item
      \begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
        \textbf{LinkedIn, Mountain View} & July 2013 - Present\\
      \end{tabular*}
      Software Engineer \\
      \vspace{3 mm}
      Led the design and implementation of MVC-based frontend architecture for a new product called Sales Navigator (\emph{\url{http://business.linkedin.com/sales-solutions/prospecting-tool.html}}). 

      Built several key features for the product, including Login, Onboarding, Search, Settings and Seat Management. The ability to run advanced searches globally from the navigation bar was one of the key features demoed by the product team and was very well received by beta customers.

    \item
      \begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
        \textbf{Department of Computer Science, Virginia Tech} & August 2011 - May 2013\\
      \end{tabular*}
      Graduate Research Assistant \\
      \vspace{3 mm}
      Built Virtual Town Square (\emph{\url{http://vts.cs.vt.edu}}), an online community for small towns which aggregates local news articles, blogs, events, Facebook posts and Twitter updates, correlates them and presents them as story mashups. 

      Built Contextinator (\emph{\url{http://contextinator.cs.vt.edu}}) for my Master's Thesis, a browser extension that lets users divide their web browsing sessions into projects and manage all their project-related information stored on the web.

    \item
      \begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
        \textbf{Khan Academy, Mountain View} & May - August 2012\\
      \end{tabular*}
      Software Developer Intern\\
      \emph{\url{http://ankitahuja.com/blog/2012/08/27/summer-at-khan-academy/}}\\
      \vspace{3 mm}
      Designed and implemented the client-side and backend implementation of a user discussion plugin that is used for all user discussions on khanacademy.org. Also, worked on user profile improvements, refactoring video page discussions, and moderation tools.
  \end{itemize}

  \vspace{0.1in}

  \textbf{Notable Projects}

  \begin{itemize}
    \setlength{\parskip}{2mm}

    \item
      \begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
        \textbf{Instasearch} - \emph{\url{https://itunes.apple.com/us/app/instasearch/id763346289?ls=1&mt=8}}\\
      \end{tabular*} \\

      \vspace{3 mm}

      An iPhone App that lets users perform fast and easy web searches by providing the ability to query once and search everywhere. It lets users swipe between results from different sites and applications. Available in the App Store.

    \item
      \begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
        \textbf{Stylebot} - \emph{\url{https://chrome.google.com/webstore/detail/oiaejidbmkiecgbjeifoejpgmdaleoha}}
      \end{tabular*} \\

      \vspace{3 mm}

      A browser extension that lets users manipulate the appearance of a webpage through a WYSIWYG interface and save their changes. Actively being used by more than 120,000 users with a 4.5 star rating from 700+ users on the Chrome Web Store.

    \item
      \begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
        \textbf{Stylebot Social} - \emph{\url{http://stylebot.me}}
      \end{tabular*} \\

      \vspace{3 mm}

      An online community for users to share and install other users’ userstyles. The site currently has over 3000 registered users and over 1700 shared styles.

    \item
      \begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
        \textbf{gleeBox} - \emph{\url{http://thegleebox.com}}
      \end{tabular*} \\
      
      \vspace{3 mm}

      A browser extension that lets users browse the web by typing commands into a prompt to simulate actions like scrolling, opening links, sharing, etc. Actively being used by more than 6000 users on Google Chrome with a 5-star rating in the Chrome Web Store.

    \item
      \begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
        \textbf{See} - \emph{\url{http://ankitahuja.com/experiments/see}}
      \end{tabular*} \\

      \vspace{3mm}

      An interactive force-directed graph visualization to explore connections between biclusters.
  \end{itemize}

  \vspace{0.1in}

  \textbf{Skills}
  \begin{itemize}
    \setlength{\parskip}{2mm}%
    \item
      \textbf{Languages}: JavaScript, Objective-C, Scala, Ruby, PHP, C++, SQL, HTML/CSS \\

    \item
      \textbf{Platforms}: Cocoa, Play, Ruby on Rails, Mac OS X, Linux \\
  \end{itemize}

  \vspace{0.1in}

  \textbf{Publications}

  \begin{itemize}
    \setlength{\parskip}{2mm}%
    \item
      \textbf{Contextinator: Project-Based Management of Personal Information on the Web} - Ankit Ahuja, Ben Hanrahan, Manuel A. Pérez-Quiñones; \emph{WEBIST - 10th International Conference on Web Information Systems and Technologies, TBA, 2014.}

    \item
      \textbf{Encouraging civic participation through local news aggregation} - Andrea Kavanaugh, Ankit Ahuja, Manuel Pérez-Quiñones, John Tedesco, and Kumbirai Madondo; \emph{Proceedings of the 14th Annual International Conference on Digital Government Research (dg.o '13). ACM, New York, NY, USA, 2013.}

    \item
      \textbf{(Hyper) local news aggregation: designing for social affordances} - Andrea Kavanaugh, Samah Gad, Sloane Neidig, Manuel A. Pérez-Quiñones, John Tedesco, Ankit Ahuja, and Naren Ramakrishnan; \emph{Proceedings of the 13th Annual International Conference on Digital Government Research (dg.o '12). ACM, New York, NY, USA, 2012.}      
  \end{itemize}

  \vspace{0.1in}

  \textbf{Talks}

  \begin{itemize}
    \setlength{\parskip}{2mm}%
    \item
      \textbf{Virtual Town Square - Building a Local Information Ecosystem} - Ankit Ahuja: Center for HCI Seminar Series, Virginia Tech, Blacksburg, VA; Feb 2013

    \item
      \textbf{Designing a Location-Based Interface for a Hyper-local News Aggregator} - Ankit Ahuja, Andrea Kavanaugh: Open Locast U Symposium, MIT Mobile Experience Lab, MIT, Cambridge, MA; Jan 2013
  \end{itemize}
\end{document}
